---
title: My Quarto Theme
author: Kazuharu Yanagimoto
date: 2023-05-25
date-format: long
title-slide-attributes:
    data-background-image: "https://source.unsplash.com/mjeQon0Mh_Q"
execute:
    echo: false
    warning: false
    message: false
    cache: false
format:
  revealjs:
    standalone: false
    embed-resources: false
    width: 1600
    height: 900
    theme: quartomonothemer.scss
    slide-number: true
    fig-cap-location: top
    fig-format: svg
    pdf-separate-fragments: false
    fig-align: center
bibliography: references.bib
url: https://kazuyanagimoto.com/quartomonothemer/vignettes/mytheme/
links:
  - name: Code
    url: https://github.com/kazuyanagimoto/quartomonothemer/blob/main/vignettes/mytheme/index.qmd
    icon: fa-brands fa-github
  - name: PDF
    url: https://kazuyanagimoto.com/quartomonothemer/vignettes/mytheme/mytheme.pdf
    icon: fa-solid fa-file-pdf
---

# Palmer Archipelago Penguin {visibility="uncounted"}

@horst_palmer_2020

```{r}
library(dplyr)
library(ggplot2)
library(forcats)
library(modelsummary)
library(fixest)
library(gt)
library(gtExtras)
library(gghighlight)
library(quartomonothemer)
library(showtext)
```


```{r}
font_title <- "Josefin Sans"
font_text <- "Montserrat"
font_sans <- "Noto Sans" 
color_base <- "#009F8C"
color_base_light <- "#95DFD6"
color_accent <- "#B75C9D"
color_accent_light <- "#DBA6CC"
gray <- "#bebebe"
darkgray <- "#6d6d6d"

# font_add_google(font_title)
# font_add_google(font_text)
showtext_auto()

style_mono_quarto(
  font_title = font_title,
  font_text = font_text,
  font_sans = font_sans,
  color_base = color_base,
  color_accent = color_accent,
  color_link = color_accent,
  color_code = color_base,
  size_base = 30,
  path_scss = here::here("vignettes/mytheme/quartomonothemer.scss")
)
```

## Bill Length

```{r}
library(palmerpenguins)
```

```{r}
penguins |>
  group_by(species) |>
  summarize(bill_length_mm = mean(bill_length_mm, na.rm = TRUE)) |>
  mutate(lbl = paste0(round(bill_length_mm), "mm")) |>
  ggplot(aes(bill_length_mm, fct_reorder(species, bill_length_mm))) +
  geom_col(fill = color_base) +
  geom_text(aes(label = lbl),
            hjust = 0, nudge_x = .5,
            size = 7, fontface = "bold", family = font_text) +
  scale_x_continuous(expand = expansion(mult = c(0, .15))) +
  labs(x = NULL, y = NULL) +
  theme_quarto() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank()) +
  gghighlight(species == "Chinstrap")
```

## Flipper and Bill Length

```{r}
penguins |>
  ggplot(aes(x = flipper_length_mm, y = bill_length_mm,
             color = species, shape = species)) +
  geom_point(size = 3) +
  scale_color_manual(values = c(color_base, color_base_light, darkgray)) +
  labs(x = "Flipper Length (mm)", y = "Bill Length (mm)") +
  theme_quarto() +
  theme(legend.position = c(0.9, 0.1))
```

## Bill Length by Sex

<br>

```{r}
gtb <- penguins |>
  filter(!is.na(sex)) |>
  group_by(species, sex) |>
  summarize(bill_length = mean(bill_length_mm, na.rm = TRUE),
            .groups = "drop") |>
  tidyr::pivot_wider(names_from = "sex", values_from = "bill_length",
                     names_prefix = "bill_length_") |>
  mutate(ratio_bar = 100 * bill_length_female / bill_length_male,
         ratio = ratio_bar / 100) |>
  gt(rowname_col = "species") |>
  cols_label(bill_length_female = "Female", bill_length_male = "Male",
             ratio_bar = "Female/Male", ratio = "Pct.") |>
  fmt_number(columns = starts_with("bill_length"), decimals = 1) |>
  fmt_percent(ratio, decimals = 0) |>
  gt_plt_bar_pct(ratio_bar, fill = color_base, scaled = TRUE) |>
  opt_table_font(font = google_font(name = font_text)) |>
  gt_theme_quarto()

gtb
```

## Bill Length by Sex {visibilty="uncounted"}

<br>

```{r}
gtb |> gt_highlight_rows(rows = 2, fill = color_base_light)
```


# Titanic Passenger Survival {visibility="uncounted"}
@hendricks_titanic_2015

```{r}
library(titanic)
titanic <- as_tibble(titanic_train) |>
  janitor::clean_names() |>
  rename(gender = sex, is_survived = survived) |>
  mutate(is_survived = is_survived == 1,
         pclass = recode_factor(pclass,
            `1` = "First",
            `2` = "Second",
            `3` = "Third"),
         gender = recode_factor(gender,
            male = "Men",
            female = "Women"),
         age_bin10 = cut(age, breaks = seq(0, 90, by = 10),
            labels = c("<10", "10-19", "21-29", "30-39", "40-49", "50-59", "60-69", "70-79", ">80"), right = FALSE),
         age_c = recode(age_bin10,
                    `60-69` = ">60",
                    `70-79` = ">60",
                    `>80` = ">60"),
         has_family = sib_sp + parch > 0
         )
```



## Survival Rate by Gender

```{r}
titanic |>
  group_by(pclass, gender) |>
  summarize(rate_survived = mean(is_survived), .groups = "drop") |>
  ggplot(aes(x = rate_survived, y = fct_rev(pclass), fill = fct_rev(gender))) +
  geom_col(position = "dodge") +
  scale_x_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(color_accent, color_base)) +
  labs(x = NULL, y = NULL) +
  theme_quarto() +
  theme(legend.position = c(0.9, 0.1),
        panel.grid.major.y = element_blank(),
        plot.margin = margin(0, 30, 0, 0)) +
  guides(fill = guide_legend(reverse = TRUE))
```

## Survival Rate by Age

```{r}
#| fig-align: center
sum_titanic <- titanic |>
  filter(!is.na(age_c)) |>
  group_by(pclass, age_c) |>
  summarize(rate_survived = mean(is_survived), .groups = "drop")

sum_titanic |>
  ggplot(aes(x = age_c, y = rate_survived, color = pclass,
             shape = pclass, group = pclass)) +
  geom_point(size = 4) +
  geom_path() +
  scale_color_manual(values = c(color_base, color_base_light, "gray")) +
  geom_text(data = filter(sum_titanic, age_c == ">60"),
            aes(label = pclass, x = age_c, y = rate_survived, color = pclass),
            hjust = -0.2,
            family = font_text,
            size = 5) +
  scale_y_continuous(labels = scales::label_percent()) +
  coord_cartesian(clip = "off", expand = FALSE) +
  labs(x = NULL, y = NULL) +
  theme_quarto() +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "none",
        plot.margin = margin(30, 80, 10, 10))
```

## Survival Rate

```{r}
sum_titanic <- titanic |>
  filter(!is.na(age_c)) |>
  group_by(pclass, gender, age_c) |>
  summarize(rate_survived = mean(is_survived), .groups = "drop")

sum_titanic |>
  mutate(lbl = paste0(round(100 * rate_survived), "%")) |>
  ggplot(aes(x = age_c, y = fct_rev(pclass), fill = gender, alpha = rate_survived)) +
  geom_tile() +
  geom_text(aes(label = lbl), color = "black", family = font_text, alpha = 1) +
  scale_fill_manual(values = c(color_base, color_accent)) +
  facet_wrap(~gender) +
  labs(x = NULL, y = NULL) +
  theme_quarto() +
  theme(panel.grid.major = element_blank(),
        axis.text.x = element_text(size = 12),
        legend.position = "none")
```

## Regression of Survival Rate

<br>

```{r}
models <- list(
    "(1)" = feols(is_survived ~ gender + has_family | pclass, data = titanic),
    "(2)" = feols(is_survived ~ gender + has_family | pclass + age_c, data = titanic),
    "(3)" = feols(is_survived ~ gender + has_family | pclass + age_c + embarked, data = titanic)
)

```

```{r}
cm  <-  c(
    'genderWomen' = "Women",
    "has_familyTRUE" = "With Family"
)

gm <- tibble(
    raw = c("FE: pclass", "FE: age_c", "FE: embarked", "nobs"),
    clean = c("FE: Class", "FE: Age Category", "FE: City Embarked", "Observations"),
    fmt = c(0, 0, 0, 0)
)

gtb <- modelsummary(models,
  output = "gt",
  star = TRUE,
  coef_map = cm,
  gof_map = gm) |>
  opt_table_font(font = google_font(name = font_text)) |>
  gt_theme_quarto()
  
gtb
```

## Regression of Survival Rate

<br>

```{r}
gtb |>
  gt_highlight_rows(rows = 1, fill = color_accent_light)
```


## Regression of Survival Rate

<br>

```{r}
gtb |>
  gt_highlight_rows(rows = 3, fill = color_base_light)
```


## References {visibility="uncounted"}
::: {#refs}
:::